p-CAPTCHAs and the Recognition Problem

### 2012-02-17 frostedglass/paper.tex
More changes

Dividing both sides of the last inequality by $n_{sp}$, we get system security when $\frac{n_f}{n_{SP}} < F(l)$. This could be accomplished by increasing $n_{SP}$, but if we could increase the size of our key space, we may as well use a traditional symmetric-key cryptosystem like AES. Thus, a p-CAPTCHA system is valuable when $n_{SP}$ is small and cannot be increased. We are trying to make the recognition problem sufficiently difficult that $F(l)$ is large. Because we are designing $R$ to give a lower score to $CI_{true}$, $F(l)$ will be largest when the distribution of $X_k$ is close to the distribution of $Y$, or in other words, when $R$ mistakenly assigns low scores to false candidate plaintexts because they look a lot like the true plaintext. This metric can be applied to any approach that attempts to recognize a true plaintext from a false one by minimizing some measurement of each candidate image, whether this is being applied to the p-CAPTCHA system presented by Laptyeva et al., the one presented below, or another approach. A framework similar to this could be applied to an attack that maximizes some measurement of each candidate image.

@@

CAPTCHAs are sometimes broken so it is worthwhile to have ideas of different approaches. Similarly, it is valuable to learn about more possible ways of creating p-CAPTCHAs in case one of them is broken. Some general things to consider when designing a p-CAPTCHA system:
\begin{itemize}
\item The variety of CAPTCHAs that one can use is smaller when trying to exploit the recognition problem because recognizing a true p-CAPTCHA plaintext will generally be easier than reading a CAPTCHA. (See Figure~{\ref{CAPTCHALevels}}.) One must have a CAPTCHA and a transformation that makes the transformed plaintexts look like the true plaintext.
\item Focus on increasing the difficulty of the recognition problem. If you use your short key to encode a lot of information about parameters, you may have less available to connect to spurious plaintexts. If an attacker could figure out that some combinations of parameters are not possible, any keys tied to those parameters could be immediately eliminated, reducing an already small key space without requiring any OCR.
\item If you are transforming an image of a strong key, be careful that the transformed image does not have recognizable parts of the strong key. For example, if the strong key is ten characters, but four of the characters can be figured out from looking at a transformed image, then at that point it may be feasible to mount a brute-force attack directly on the strong key which now has only six unknown characters.
\end{itemize}

@@

Noise was added to the image in step two in order to increase the difficulty of finding edges. When a letter is cut into pieces and those pieces are shifted around, the total amount of letter edge length will likely increase. If edges were easily discernible, the plaintext would be recognizable because it would have less total edge length. Decryption simply requires finding the inverse of the permutation corresponding to SP and rearranging the blocks into their original, human-readable form.

The p-CAPTCHA plaintext in Figure~{\ref{EncryptionProcess}} was encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

@@

Some parameters of this system could be adjusted, such as the size of the characters, the amount of fuzziness (noise) in the background and in the characters, and the size of the tiles that get permuted. By adjusting these parameters, we can better position ourselves in the window of possible images that are too difficult for a human to recognize, but still possible for a human to read without confusing the characters.

Some care should be taken when choosing parameters. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of characters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what characters were being used by looking at a scrambled image. By entering these characters into the computer, the computer could then try a brute force attack with permutations of these characters without needing to solve any OCR problem.

>>>>

Dividing both sides of the last inequality by $n_{sp}$, we get system security when $\frac{n_f}{n_{SP}} < F(l)$. This could be accomplished by increasing $n_{SP}$, but if we could increase the size of our key space, we may as well use a traditional symmetric-key cryptosystem like AES. Thus, a p-CAPTCHA system is valuable when $n_{SP}$ is small and cannot be increased. We are trying to make the recognition problem sufficiently difficult that $F(l)$ is large. Because we are designing $R$ to give a lower score to $CI_{true}$, $F(l)$ will be largest when the distribution of $X_k$ is close to the distribution of $Y$, or in other words, when $R$ mistakenly assigns low scores to false candidate plaintexts because they look a lot like the true plaintext.

This metric can be applied to any approach that attempts to recognize a true plaintext from a false one by minimizing some measurement of each candidate image, whether this is being applied to the p-CAPTCHA system presented by Laptyeva et al., the one presented in this paper, or another approach. The actual shapes of the score distributions for a given recognition oracle, and the parameters of those distributions, should be measured empirically. A framework similar to this could be applied to an attack that maximizes some measurement of each candidate image.

@@

CAPTCHAs are sometimes broken so it is worthwhile to have ideas of different approaches. Similarly, it is valuable to learn about more possible ways of creating p-CAPTCHAs in case one of them is broken. Some general things to consider when designing a p-CAPTCHA system:
\begin{itemize}
\item The variety of CAPTCHAs that one can use is smaller when trying to exploit the recognition problem because recognizing a true p-CAPTCHA plaintext will generally be easier than reading a CAPTCHA. (See Figure~{\ref{CAPTCHALevels}}.) One must have a CAPTCHA and a transformation that makes the transformed plaintexts look like the true plaintext.
\item The computer will not have to filter through more candidate plaintexts than the number of decryption keys. We assume that the attacker has access to the decryption algorithm, in which case the attacker could put each possible key into the decryption algorithm and set the recognition oracle to the corresponding image.
\item Focus on increasing the difficulty of the recognition problem. If you use your short key to encode a lot of information about parameters, you may have less available to connect to spurious plaintexts. If an attacker could figure out that some combinations of parameters are not possible, any keys tied to those parameters could be immediately eliminated, reducing an already small key space without requiring any OCR.
\item If you are transforming an image of a strong key, be careful that the transformed image does not have recognizable parts of the strong key. For example, if the strong key is ten characters, but four of the characters can be figured out from looking at a transformed image, then at that point it may be feasible to mount a brute-force attack directly on the strong key which now has only six unknown characters.
\end{itemize}

@@

Noise was added to the image in step two in order to increase the difficulty of finding edges. When a letter is cut into pieces and those pieces are shifted around, the total amount of letter edge length will likely increase. If edges were easily discernible, the plaintext would be recognizable because it would have less total edge length. Decryption simply requires finding the inverse of the permutation corresponding to SP and rearranging the tiles into their original, human-readable form.

The p-CAPTCHA plaintext in Figure~{\ref{EncryptionProcess}} was encrypted by permuting 57 tiles. Although there are 57-factorial permutations of 57 tiles, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Even a small number of tiles will be sufficient to have a unique permutation for each key, so tile size should be chosen to make the recognition problem more difficult.

@@

Some parameters of this system could be adjusted, such as the size of the characters, the amount of fuzziness (noise) in the background and in the characters, and the size of the tiles that get permuted. By adjusting these parameters, we can better position ourselves in the window of possible images that are too difficult for a computer to recognize, but still possible for a human to read without confusing the characters.

Some care should be taken when choosing parameters. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of characters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what characters were being used by looking at a scrambled image. By entering these characters into the computer, the computer could then try a brute-force attack with permutations of these characters without needing to solve any OCR problem. Candidate plaintexts could easily be made more difficult to recognize by increasing the number of XOR operations on the pixels, making the image "fuzzier". Unfortunately, doing so makes the true plaintext harder for a human to read, so which risks making characters hard for a human to differentiate.

A few approaches may be taken to attack the p-CAPTCHA system presented here.
